Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-30 tex/comments/2-nat-comments.tex
Kernel e>n+r+1 comments

@@

In this section, we characterize $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ for $e \nmid n + r + 1$ and for $e=n+r+1$. When the representation is clear, we will simply denote this kernel as $K$ or $\cap\text{ker}(1+T_i)$. For compactness, in this section we use $\sim $ to denote "proportional to". For convenience, define $M_0^0$ to be the zero representation.

\subsubsection{Proposition \ref{Trivial}}
\label{kernel}
\begin{definition}

	Fix some basis element $\psi\in M_{2n+r}^r$. For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$. Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$. This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$. See \ref{sub-matching example}.

	If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $\psi(a,b)$ will always refer to those nodes and they're matchings, though it may not be a sub-matching unless specified. For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.

@@

\begin{figure} 
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{4}{1/4, 2/3}
		\end{gathered}}$
	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. $\psi(2,5)$ is not a sub-matching.}
	\label{sub-matching example}
\end{figure}

Define the rainbow element $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left then a rainbow.

\begin{proposition}
	Let $w$ be an arbitrary vector in $M_{2n+r}^r$. I claim that if $w\in \cap\text{ker}(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero.

	\label{rainbow nonzero}
\end{proposition}

\begin{proof}
	Let $Y$ be the set of basis elements with nonzero coordinate in $w$. Let $z$ be the greatest integer such that there exists $y\in Y$ where $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$. In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.

	Suppose $z<r$. Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y)=0$. In other words, $i_y$ is the position of the next leftmost anchor in $y$.  Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$. Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\text{ker}(1+T_i)$. To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$. $y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$. If $x\in Y,\not\in U$, the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$. If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$. Since this is the only match altered by action of $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$. So if $z<r$ $w$ is not in the desired kernel.

	Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$). Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$. Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$. Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$. Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$. I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel. $u'$ still has $r$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$. If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$. Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+i)=2n+2r-i+2$ for all $i\leq t$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$. If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$). These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$. Thus we have proved that if $R\not\in Y$, $w$ is not in the kernel.

@@

Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively. Examples are pictured in \ref{shifted rainbow}. Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.

\begin{figure}
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/2,3/8,4/7,5/6}
		\end{gathered}}$
	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
	\label{shifted rainbow}
\end{figure}

@@

\begin{proposition}
	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation. Let $y$ be a basis element with coordinate $c$ in $w$. Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element. Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively). The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.

@@

Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.

@@

\textit{Proof of lemma.}

\begin{align*}
Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
\end{align*}

Now let us prove the proposition.

\begin{proof}
	Consider acting on $w$ by an element $(1+T_z)$. The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$. Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.

	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$. Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$. This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}. I claim the following:

	\begin{center}
		\textit{claim}:
		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.

@@

	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}. Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition. Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching. Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$. If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor. All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$. Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$. For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$. Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information. Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors. Thus the claim is proved.

	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:

@@

	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$. By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}. $\theta_i$ is an identical proof, so the proposition follows.

@@

We are now ready to prove proposition \ref{Trivial}.

\begin{proof}
	Suppose $\cap\text{ker}(1+T_i)=K\not=0$. Take nonzero $w\in K$. By Proposition \ref{rainbow nonzero}, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$. By proposition \ref{shifted rainbow coeffs}, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.

@@

\subsubsection{Kernel Basis}

@@

	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$. Let $w\in\cap\text{ker}(1+T_i)$. MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}). Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.

@@

\begin{corollary}
	Let $w\in\cap\text{ker}(1+T_i)$, $w\not=0$. Suppose $\psi(1,a)$ is a sub-matching with no anchors. Then:

@@

\vspace{5mm}
\begin{theorem}
	Suppose $e=n+r+1$. Then $\cap\text{ker}(1+T_i)\not=0$.
	\label{kernel existence}
\end{theorem}

>>>>

{\color{magenta} We can make this section-level and work it out, I'm sure.}

@@

{\color{magenta} Better subsection label: Sign Subrepresentations of $M$. If used, should remind the reader in the beginning that $K$ is a direct sum of all sign subrepresentations (by dimensionality, just a sign representation if it's nonzero).}

In this section, we characterize $K_{2n+r}^r := \bigcap_{i=1}^{2n+r-1} \ker (1 + T_i) = \ker \bigoplus_{i = 1}^{2n + r - 1} (1 + T_i)$ for $e \nmid n + r + 1$ and for $e=n+r+1$. When the representation is clear {\color{magenta} When the indices $2n + r, r$ are clear\ldots}, we will simply denote this kernel as $K$ or $\cap\ker(1+T_i)$. For compactness, in this section we use $\sim $ to denote "proportional to". For convenience, define $M_0^0$ to be the zero representation.
{\color{magenta} Replace $\backslash$text\{ker\} with $\backslash$ker;
I've done it for this document already.}

{\color{magenta} Next section needs new name (perhaps ``The case $e \nmid n+r+1$''?) We can handle the reference 3.3 -> this section near proposition 3.3, and perhaps even name 3.3 by it's name in this section.}
\subsubsection{Proposition \ref{Trivial}}
\label{kernel}
\begin{definition}

	Fix some basis element $\psi\in M_{2n+r}^r$. For $1 \leq a,b \leq 2n + r$ define $\psi(a):=b$ iff $a$ and $b$ are matched in $\psi$, $\psi(a):=a$ if $a$ is an anchor in $\psi$. Given that $\psi$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $\psi(a,b)$ of $\psi$ to be the basis element $\sigma\in M_{b-a+1}^{r'}$ specified by $\sigma(i)=\psi(i+a-1)-a+1$. This sub-matching is defined for $a<b$ when $\psi(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$. See \ref{sub-matching example}.
  {\color{magenta} For anybody reading via paper or something not handling hrefs, it's better to refer to this as Figure \ref{sub-matching example}.}

  {\color{magenta} use $\backslash$emph for emphasis (in this environment, it will be italicized)}

  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, {\color{magenta} for nodes $a,b$ satisfying $a \leq b$ (or $1 \leq a \leq b \leq 2n+r)$.}$\psi(a,b)$ will always refer to those nodes and they're {\color{magenta} their} matchings, though it may not be a sub-matching unless specified.{\color{magenta} No need to say ``unless specified''} For any other $a,b$, we define $\psi(a,b)$ to be an element of the representation with no nodes.{\color{magenta} What other $a,b$? Is this $a > b$, $a,b \notin \cbr{1,\dots,2n+r}$, etc? Also, can this just be defined the unique element of the zero representation?}

@@

\begin{figure} 
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{6}{1/2, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{4}{1/4, 2/3}
		\end{gathered}}$
	\caption{$\psi\in M_6^0$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. $\psi(3,6)=\sigma$. 
    {\color{magenta} and }
  $\psi(2,5)$ is not a sub-matching.}
	\label{sub-matching example}
\end{figure}

Define the rainbow element 
{\color{magenta} $\backslash$emph.} 
$R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left then a rainbow.
{\color{magenta} to the left, followed by a ``rainbow'' on the right.}

\begin{proposition}
  Let $w$ be an arbitrary vector in $M_{2n+r}^r$.
  {\color{magenta} No need to say ``arbitrary.''} 
  I claim that if $w\in \cap\ker(1+T_i)$, the coordinate $c$ of the rainbow element $R$ in $w$ is nonzero. 
  {\color{magenta} No need to say ``I claim.''}
	\label{rainbow nonzero}
\end{proposition}

\begin{proof}
  Let $Y$ be the set of basis elements 
  {\color{magenta} of $M_{2n + r}^r$} 
  with nonzero coordinate in $w$. 
  Let $z$ be the greatest integer such that there exists $y\in Y$ where 
  {\color{magenta} some element $y \in Y$ satisfying\ldots} 
  $y(1)-1=...=y(z)-z=0$, and let $U\subset Y$ be the set of such $y$. 
  In other words, $U$ is the set of basis elements in $Y$ which have the most anchors to the far left.

	Suppose $z<r$. 
  Then for each $y\in U$ there exists a minimal $i_y>z+2$ such that $y(i_y) =0$ 
  {\color{magenta} $y(i_y) = i_y$, or just $y$ contains an anchor at $i_y$}. 
  In other words, $i_y$ is the position of the next leftmost anchor in $y$.
  {\color{magenta} totally subjective, buy I would put a new paragraph here.}

  Fix $\tilde{y}$ such that $i_{\tilde{y}}\leq i_y$ for all $y$. 
  {\color{magenta} Is this just some $\tilde y$ for each $y$?}
  Then I claim the basis element $y':=q^{-1/2}(1+T_{i_{\tilde{y}}-1})\tilde{y}$ has nonzero coordinate in $(1+T_{i_{\tilde{y}}-1})w$, implying $w\not\in \cap\ker(1+T_i)$.
  {\color{magenta} Rather than ``I claim\ldots to see this'', say something like ``We will show\ldots to do so''}
  To see this, we can show that $\tilde{y}$ is the only basis element in $Y$ such that $(1+T_{i_{\tilde{y}}-1})\tilde{y}\sim y'$. $y'$ still has $z$ anchors on the left, and $i_{y'}<i_{\tilde{y}}$, so $y'\not\in Y$.
  If $x\in Y,\not\in U$,
  {\color{magenta} If $x \in Y$ and $x \not\in U$, then\ldots}
  the basis element $x'$ proportional to $(1+T_{i_{\tilde{y}}-1})x$ will have $k$ anchors at the far left only if the next anchor is at a position $i_{x'}>i_{\tilde{y}}$, so it cannot be $y'$. If $x\in U$, $x'$ will have anchor at $i_{y'}$ if and only if $i_x=i_{\tilde{y}}$ and $x(i_{\tilde{y}})=\tilde{y}(i_{\tilde{y}})$. Since this is the only match altered by action of $(1+T_{i_{\tilde{y}}-1})$ on $x$, if $(1+T_{i_{\tilde{y}}-1})x\sim y'$ this implies $x=\tilde{y}$. So if $z<r$ $w$ is not in the desired kernel.
  {\color{magenta} Nice.}

  {\color{magenta} I think a very short vspace would be nice here.}
	Suppose $z=r$ but $R\not\in U$ (so $R\not\in Y$).
  {\color{magenta} Doesn't $U$ just depend on $z$, so that $R \in U$ whenever $z=r$?}
  Let us define a sequence of subsets of $U$ in the following way: $U_0:=U$, $U_{i+1}:=\{u\in U_i| u(r+i+1)=2n+2r-i+1 \}$. Since $R\not\in U$, $\exists t<n-1$ such that $U_{t+1}=\emptyset$. 
  {\color{magenta} Don't need ``let us.''}
  Choose $\tilde{u}\in U_t$ such that $\tilde{u}(r+t+1)\geq u(r+t+1)$ for all $u\in U_t$. Consider the basis element $u':=q^{-1/2}(1+T_{\tilde{u}(r+t+1)})\tilde{u}$.

  {\color{magenta} No ``I claim.'' Also, I would put a new paragraph here, or after the next line (fair if you disagree). Also, maybe say that this is analogous to before.}
  I claim that $\tilde{u}$ is the only element in $Y$ such that $(1+T_{\tilde{u}(r+t+1)})\tilde{u}\sim u'$, again implying that $w$ is not in the desired kernel. $u'$ still has $r$ anchors on the left, $u'(r+i)=2n+2r-i+2$, $1\leq i\leq t$, and $u'(r+t+1)>\tilde{u}(r+t+1)$, so $u'\not\in Y$. If $x\in Y,\not\in U$,  the basis element $x'$ proportional to $(1+T_{\tilde{u}(r+t+1)})x$ will have $r$ leftmost anchors only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$. Similarly, if $x\in U,\not\in U_t$, the basis element $x'$ will have the property $x'(r+i)=2n+2r-i+2$ for all $i\leq t$ only if $x'(r+t+1)<\tilde{u}(r+t+1)$, so $x'\not=u'$. If $x\in U_t$, $x'(r+t+1)=u'(r+t+1)$ if and only if $x(r+t+1)=\tilde{u}(r+t+1)$ and $x(x(r+t+1)+1)=\tilde{u}(\tilde{u}(r+t+1)+1)$ (since $u'\not \in Y$). These are the only matches altered by the action $(1+T_{\tilde{u}(r+t+1)})$, so this implies $x=\tilde{u}$. Thus we have proved that if $R\not\in Y$, $w$ is not in the kernel.

@@

{\color{magenta} This might read better as ``Let $R_{r,i},R_{L_i}$ be the basis elements formed by ''moving.``
Also, it may be nice to just define it formally and point to Figure \ref{shifted rainbow};
the moving analogy is clear from the figure.
}
Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively. Examples are pictured in {\color{magenta} Figure \ref{shifted rainbow}}. Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.{\color{magenta} align might be nicef for these definitions}

\begin{figure}
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/2,3/8,4/7,5/6}
		\end{gathered}}$
	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right
  {\color{magenta} The elements $R_{L,0},\dots,R_{L_3} \in W_8^0$ are\ldots}
}
	\label{shifted rainbow}
\end{figure}

@@

\begin{proposition}
  Let $w$ be an element in the kernel 
  {\color{magenta} probably good to refer to it as $K$, or remind the reader of the indices on $T$. Also, why the subscript $T_z$?
  In general, we may shorten this to ``Let $w$ be an element in $K \subset M$'' to get down on the length of this proposition.
}
  intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation. Let $y$ be a basis element with coordinate $c$ in $w$. 
  {\color{magenta} Better to say ``there exist'' for proposition statements.
  Also, the reader probably knows what $R$ is by now? Maybe it's good to leave it in, idk, but this statement is already very wordy.
}
  Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element. 
  {\color{magenta} If it's still too wordy, maybe move the definition of $\theta,\phi$ outside of the statement? Idk.}
  Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively). The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.

@@

Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.
{\color{magenta}We will use the following algebraic lemma\ldots.
Also, the reader knows that you're stating it, no need to tell them.
}

@@

\begin{proof}[Proof of lemma]
\begin{align*}
Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
\end{align*}
\end{proof}

{\color{magenta} Nice proof.
Can be specified by using $\backslash$begin\{proof\}[Proof of lemma], as I've fixed in the text here.}

Now let us prove the proposition.
{\color{magenta} we will\ldots
Guiding text may 
}

\begin{proof}
  Consider acting on $w$ by an element $(1+T_z)$. The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$. Specifically, it will be $(1+q)c\iota+(q^{1/2})\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.
  {\color{magenta} fixed exponent on $q^{1/2}$.}

  Let $n:=a+b-1$ and {\color{magenta} let } $r$ be the number of anchors in $y(a,b)$. Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$. This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in {\color{magenta} Figure }\ref{shifted relations}. 
  I claim the following:
  {\color{magenta} Avoid ``I claim''}

  {\color{magenta} put in claim* environment}
	\begin{center}
		\textit{claim}:
		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.

@@

  {\color{magenta} $\backslash$begin\{proof\}[Proof of claim], avoid ``let us'' throughout}

	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$,
  {\color{magenta} awkward wording}
  as shown in 
  {\color{magenta} Figure} 
  \ref{shifted relations}. Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition. Me
  {\color{magenta} typo} 
  note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching. Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$. If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor. All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$. Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$. For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$. Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information. Lastly, note that our argument 
  {\color{magenta} \ldots the above argument was \ldots and hence an analogous argument without anchors illustrates the $\theta_i$ case.}
  was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors. Thus the claim is proved.
	  {\color{magenta} three ideas for this:
    first: break into smaller paragraphs.
    Second: assign a variable to $a - 1 +  + n/2$ for clarity.
    Third: here and elsewhere, when saying a dense statement, examine whether it's good to put an intuitive statement for it before, after, or if it's more clear/concise to not include it at all.
  }

  Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction
  {\color{magenta} on $i$}:

@@

  {\color{magenta} Suppose \ldots then,}
	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$. By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}. $\theta_i$ is an identical proof, so the proposition follows.

@@

We are now ready to prove proposition \ref{Trivial}.
{\color{magenta} Restate the proposition. I will reference forward to this part.
  Upon rereading this in the new structure, I actually do agree with you that we could just do away with Proof 2.
  With the last batch of edits, this is so much more manageable and clear (and less technical) than I remembered it being.
}

\begin{proof}
	Suppose $\cap\ker(1+T_i)=K\not=0$.
  {\color{magenta} More usual to say $K := \cap \ker(1 + T_i) = 0$.}
  Take nonzero $w\in K$. By Proposition \ref{rainbow nonzero}, the coordinate of the rainbow vector $R$ is nonzero; suppose the coordinate is $c$. By proposition \ref{shifted rainbow coeffs}, the coordinates of the basis elements $R_{L,n+r-1}$ and $R_{L,n+r-2}$ are $Q_{n+r-1}c$ and $Q_{n+r-2}c$ respectively.

@@

{\color{magenta} New name, such as ``Charactrizing $K$'' or ``Characterizing the sign subrepresentations.''
Also, lowercase section titles.}
\subsubsection{Kernel Basis}

@@

	Let $M_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$. Let $w\in\cap\ker(1+T_i)$. MLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition \ref{rainbow nonzero}). Then the coordinate of any basis element $\psi\in M_{2n+r}^r$ in $w$ is $x_{\psi}(q)$.

@@

\begin{corollary}
	Let $w\in\cap\ker(1+T_i)$, $w\not=0$. Suppose $\psi(1,a)$ is a sub-matching with no anchors. Then:

@@

\vspace{5mm}
\begin{theorem}
	Suppose $e=n+r+1$. Then $\cap\ker(1+T_i)\not=0$.
	\label{kernel existence}
\end{theorem}
